\documentclass{article}
%\usepackage{hyperref}

\usepackage{xcolor}
\usepackage[colorlinks = true,
            linkcolor = blue,
            urlcolor  = blue,
            citecolor = blue,
            anchorcolor = blue]{hyperref}

%\textheight 300mm
%\setlength{\topmargin}{0 in}
%\setlength{\oddsidemargin}{0in}
%\setlength{\evensidemargin}{0in}
%\baselineskip 7mm
%\usepackage{lipsum}
%\usepackage{enumitem}

\usepackage[a4paper, total={6in, 10in}]{geometry}



\begin{document}

\centerline{\LARGE{\textbf{Error propagation in charm baryon spectroscopy}}}
\smallskip
\centerline{Andres Ramirez-Morales and Hugo Garcia-Tecocoatzi}

\section*{Introduction}

Mass model Hamiltonian that determines the mass splitting of the charm baryon states.
\begin{equation}
\label{eqn:mass}
H = H_{\mathrm{h.o.}} + \textcolor{red}{A}\mathbf{S}^{2} + \textcolor{red}{B}\mathbf{S\cdot L} +  \textcolor{red}{E}\mathbf{I}^{2} + \textcolor{red}{G}\mathbf{C_{2}}(\mathrm{SU(3)_{f}})
\end{equation}

\section*{Parameter determination and error propagation (paper version)}

The experimentally observed charm baryon states, $\Omega_{C}$, $\Lambda_{C}$, $\Xi_{C}$, were fitted to the model described in Equation \ref{eqn:mass} to obtain the parameters $\omega, A, B, E, G$. The fitted model parameters minimize the sum of the squared differences between the experimental and model predicted masses (least squares method).\\

The measured baryon masses are reported with statistical and systematic uncertainties. To account for these uncertainties into our fitted model parameters, we carried out a statistical error propagation, that is, we randomly sampled the experimental masses, utilizing a Gaussian shape distribution having a mean equal to the central mass value and with a width equal to the squared sum of the uncertainties. We fit the model parameters using a sampled mass, corresponding to each experimental observed state, and repeat the procedure $10^5$ times. In this manner, we obtained a Gaussian distribution (a formal normality test was performed as a cross-check) for each model parameter; next, we assign the mean of the distribution as the value of the parameter and used the quantile at 68\% C.L. to extract the uncertainty. The procedure just described is referred to as Monte Carlo bootstrap uncertainty propagation [Aqui citamos al fernandez y los papers que el da].

First we performed the fit including all the available masses, this a test, to see if we can modify text and commit to the repo.

\section*{Parameter determination and error propagation (long version)}


%


\begin{thebibliography}{9}

\bibitem{energy} 
M. Farina,  $et.\,al.$,
\textit{Energy helps accuracy: electroweak precision tests at hadron colliders}.
Phys. Lett. B. \textbf{772}, 210-215 (2017),
\url{https://doi.org/10.1016/j.physletb.2017.06.043}

\bibitem{EDM}
V. Andreev, $et.\,al.$, (ACME Collaboration)
\textit{Improved limit on the electric dipole moment of the electron}.
Nature \textbf{562}, 355-360(2018),
\url{https://www.nature.com/articles/s41586-018-0599-8}

\bibitem{belle1}
K. Abe, $et.\,al.$, (BELLE Collaboration)
\textit{Observation of Large CP Violation in the Neutral B Meson System}.
Phys. Rev. Lett. \textbf{87}, 091802(2001),
\url{https://journals.aps.org/prl/abstract/10.1103/PhysRevLett.87.091802}

\bibitem{belle2}
I. Adachi, $et.\,al.$, (BELLE Collaboration)
\textit{Precise Measurement of the $CP$ Violation Parameter $\mathrm{sin}﻿2{\ensuremath{\phi}}_{1}$ in ${B}^{0}\ensuremath{\rightarrow}(c\overline{c}){K}^{0}$ Decays}.
Nature \textbf{108}, 171802(2012),
\url{https://journals.aps.org/prl/abstract/10.1103/PhysRevLett.108.171802}

\bibitem{npdgamma}
D. Blyth, $et.\,al.$, (NPDGamma Collaboration),
\textit{First Observation of $P$-odd $\ensuremath{\gamma}$ Asymmetry in Polarized Neutron Capture on Hydrogen}.
Phys. Rev. Lett. \textbf{121},  242002 (2018)
\url{https://link.aps.org/doi/10.1103/PhysRevLett.121.242002} 
 
\bibitem{QWSE}
A. Ramirez-Morales, $et.\,al.$,
\textit{Improvement of the quantum confined Stark effect characteristics by means of energy band profile modulation: The case of Gaussian quantum wells},
Journal of Applied Physics  \textbf{110}, 103715 (2011)
\url{https://doi.org/10.1063/1.3662907}

\bibitem{n3he}
M. Gericke,
\textit{The n3He experiment: Hadronic parity violation in cold neutron capture on 3He},
Proceedings of Science \textbf{253}, (2016)
\url{https://doi.org/10.22323/1.253.0102}

\bibitem{highZ}
M. Aaboud $et\,al.$ (ATLAS Collaboration),
\textit{Measurement of the double-differential high-mass Drell-Yan cross section in pp collisions at $\sqrt{s}=8$ TeV with the ATLAS detector},
J. High Energ. Phys.  \textbf{2016:9} (2016)
\url{https://doi.org/10.1007/JHEP08(2016)009}

\bibitem{primes}
M. Aaboud $et\,al.$ (ATLAS Collaboration),
\textit{Combination of searches for heavy resonances decaying into bosonic and leptonic final states using 36 fb$^{-1}$ of proton-proton collision data at $\sqrt{s}=13$ TeV with the ATLAS detector},
Phys. Rev. D \textbf{98}, 052008 (2018)
\url{https://journals.aps.org/prd/abstract/10.1103/PhysRevD.98.052008}

\bibitem{stat}
B. Laforge and L. Schoeffel,
\textit{Elements of statistical methods in high-energy physics analyses},
Nuclear Instruments and Methods in Physics Research Section A \textbf{394} 115-120 (1997)
\url{https://doi.org/10.1016/S0168-9002(97)00649-9}

\bibitem{uncBelle}
J. Charles $et al.$,
\textit{Modeling theoretical uncertainties in phenomenological analyses for particle physics},
The European Physical Journal C, \textbf{214}, 1434-6052(2017)
\url{https://doi.org/10.1140/epjc/s10052-017-4767-z}

\bibitem{ewSys}
P. Langacker and M. Luo,
\textit{Implications of precision electroweak experiments for $m_{t}$, $\rho_0$, $\sin^2\theta_W$, and grand unification},
Phys. Rev. D \textbf{44}, 3 (1991)
\url{https://doi.org/10.1103/PhysRevD.44.817}


\bibitem{NN1}
D. Guest, $et.\,al.$,
\textit{Deep Learning and Its Application to LHC Physics},
Annual Review of Nuclear and Particle Science  \textbf{68}, 161-181(2018)
\url{https://doi.org/10.1146/annurev-nucl-101917-021019}

\bibitem{NN2}
K. Albertsson, $et.\,al.$,
\textit{Machine Learning in High Energy Physics Community White Paper},
\url{https://arxiv.org/abs/1807.02876}


\bibitem{machine}
A. Radovic, $et.\,al.$,
\textit{Machine learning at the energy and intensity frontiers of particle physics},
Nature \textbf{560}, 41-48(2018)
\url{https://doi.org/10.1038/s41586-018-0361-2}

\bibitem{vector}
A. Bevan,  $et.\,al.$,
\textit{Support Vector Machines and generalisation in HEP},
Journal of Physics: Conference Series, \textbf{898}, 072021 (2017)
\url{https://doi.org/10.1088\%2F1742-6596\%2F898\%2F7\%2F072021}


\bibitem{keck}
T. Keck,  $et.\,al.$,
\textit{The Full Event Interpretation},
Computing and Software for Big Science, \textbf{6}, 2510-2044(2019)
\url{https://doi.org/10.1007/s41781-019-0021-8}


\bibitem{belleII}
B.A. Shwartz $et al.$, (Belle II collaboration)
\textit{The Belle II Experiment},
Nuclear and Particle Physics Proceedings \textbf{260} 233-237 (2015)
\url{https://doi.org/10.1016/j.nuclphysbps.2015.02.049}


\bibitem{beRes1}
M. Berger et at., (Belle collaboration)
\textit{Measurement of the decays ${\mathrm{\ensuremath{\Lambda}}}_{c}\ensuremath{\rightarrow}\mathrm{\ensuremath{\Sigma}}\ensuremath{\pi}\ensuremath{\pi}$ at Belle}
Phys. Rev. D \textbf{98}, 112006 (2018)
\url{https://journals.aps.org/prd/abstract/10.1103/PhysRevD.98.112006}


\bibitem{beRes2}
B.G. Fulsom et at., (Belle collaboration)
\textit{Observation of $\mathrm{\ensuremath{\Upsilon}}(2S)\ensuremath{\rightarrow}\ensuremath{\gamma}{\ensuremath{\eta}}_{b}(1S)$ Decay}
Phys. Rev. Lett. \textbf{121}, 232001 (2018)
\url{https://journals.aps.org/prl/abstract/10.1103/PhysRevLett.121.232001}

\bibitem{lattice}
Zachary S. Brown, $et. al.$,
\textit{Charmed bottom baryon spectroscopy from lattice QCD}
Phys. Rev. D \textbf{90}, 094507 (2014)
\url{https://journals.aps.org/prd/abstract/10.1103/PhysRevD.90.094507}

\bibitem{lepton}
Simone Bifani $et. al.$ 
\textit{Review of lepton universality tests in B decays}
J. Phys. G: Nucl. Part. Phys. \textbf{46} 023001 (2019)
\url{https://iopscience.iop.org/article/10.1088/1361-6471/aaf5de}

\bibitem{lv1}
A. Gouvea and P. Vogel,
\textit{Lepton Flavor and Number Conservation, and Physics Beyond the Standard Model}
\url{https://arxiv.org/pdf/1303.4097.pdf}

\bibitem{lv2}
A. Abdesselam $et al.$,(Belle collaboration)
\item{Test of lepton flavor universality in $B\rightarrow K^{*}l^{+}l^{-}$ decays at Belle}
\url{https://arxiv.org/abs/1904.02440}




\end{thebibliography}

\end{document}



%\bibitem{atlasM} 
%A. Yamamoto, $et.\,al.$, 
%\textit{The ATLAS central solenoid}.
%Nuclear Instruments and Methods in Physics Research Section A \textbf{584}, 53-74 (2008)
%\url{https://doi.org/10.1016/j.nima.2007.09.047}

%\bibitem{muSys}
%K. Melnikov,
%\textit{On the theoretical uncertainties in the muon anomalous magnetic moment},
%International Journal of Modern Physics A, \textbf{16}, No. 28 (2001)
%\url{https://doi.org/10.1142/S0217751X01005602}
